NumPy---Array Computation for Python

### 2019-12-17 paper.tex
STY: (array_function) Use tightlist for array-like enumeration
Start funding section

% BIDS -- UCB, CZI -- NumFOCUS/QuanSight, Tidelift, ...

>>>>

Historically, NumPy was developed primarily by voluteers in their free time.
% some funding at Berkeley, the documentation project, Travis funding ...
Over the last few years, there has an increase in paid full-time developers due
to new sources of funding.

% how much do we say about who these developers are and
% lessons learned?

% BIDS -- UCB
% https://www.moore.org/grant-detail?grantId=GBMF5447
% $645,020 in 2016
% https://sloan.org/grant-detail/8222
% $659,359 in 2017
% https://bids.berkeley.edu/news/bids-receives-sloan-foundation-grant-contribute-numpy-development

The Berkeley Institute for Data Science (BIDS) received two grants to support
the development of NumPy.
At the end of 2016, the Gordon and Betty Moore Foundation awarded them
\$645,020 for improving NumPy for better data science.
In 2017, the Alfred P. Sloan Foundation complemented the funding with an
additional \$659,359.
Stéfan van der Walt, a senior research data scientist at BIDS and a member of
the NumPy steering committee, is the PI of both grants and manages a team of
four programmers working on the project.

% technical focus 
% improve various aspects of NumPy, including easier construction of custom data types (e.g., missing values, physical units, times & dates) and better integration with arrays customized for specialized domains (e.g., SciPy's sparse arrays, pandas' DataFrames, and xarray's labeled arrays). 
% technical work, and it increased the velocity of the projects by ~25-30%, and in addition it enabled integrating some larger changes, like the numpy.random redesign.

% CZI -- NumFOCUS/QuanSight
% https://chanzuckerberg.com/eoss/proposals/strengthening-numpys-foundations-growing-beyond-code/
% NumPy and OpenBLAS received $195,000 in 2019
% https://labs.quansight.org/blog/2019/11/numpy-openblas-CZI-grant/

NumFOCUS received a grant for \$195,000 in 2019 for the development of NumPy
and OpenBLAS from the Chan Zuckerberg Initiative. 
Ralf Gommers, the Director of Quansight Labs and a member of
the NumPy steering committee, is the PI.

% focus on better serve NumPy's large number of beginner to intermediate level users
% focusing all our time on growing the team and better serving new users and contributors

% Tidelift, ...
% https://tidelift.com/subscription/pkg/pypi-numpy
% $10,000 over 24 months according to 
% https://mail.python.org/pipermail/numpy-discussion/2018-September/078736.html
